Packaging research artefacts with RO-Crate

### 2022-01-01 latex/ro-crate.tex
associated with

However the primary purpose of the RO-Crate specification is to assist
developers in leveraging Linked Data principles for the focused purpose
of describing Research Objects in a structured language, while reducing
the steep learning curve otherwise associated in Semantic Web
adaptation, like development of ontologies, identifiers, namespaces,
and RDF serialization choices.
\subsubsection{Ensuring simplicity}% {#simplicity}

>>>>

However the primary purpose of the RO-Crate specification is to assist
developers in leveraging Linked Data principles for the focused purpose
of describing Research Objects in a structured language, while reducing
the steep learning curve otherwise associated with Semantic Web
adaptation, like development of ontologies, identifiers, namespaces,
and RDF serialization choices.
\subsubsection{Ensuring simplicity}% {#simplicity}
